### 2018-08-22 Sections/economics_of_the_quantum_internet.tex
Reshuffled economics for scotty's stuff

Any asset, dividend, derivative or other financial instrument will inevitably be subject to taxation. Any form of taxation has multiplier effects as the cost markup is repeatedly handed from one market participant to the next, influencing the chain of supply and demand along the way. However, this multiplier and other economic consequences are highly dependent on the asset undergoing transaction -- the economic implications of personal income tax are quite different to those of capital gains tax.

This demonstrates that the computational power of classical networks is simply inversely proportional to the rate of taxation, i.e a linear tax performance multiplier, as we intuitively expect. And for quadratic scaling functions the dependence is inverse quadratic in the taxation rate. In both cases the multiplier is a constant factor, independent of the network size. However, for exponential scaling functions we observe an exponential dependence on both the rate of taxation and the size of the network, shown in Fig.~\ref{fig:tax_exp}(top). Note that for large networks executing computations with exponential scaling functions, there is enormous sensitivity to variations in tax rates, yielding very high leverage in computational return by tax rates.

However, taxation could also be negative, in the form of subsidisation. In Fig.~\ref{fig:tax_exp}(bottom) we focus on the region surrounding neutral taxation, showing small degrees of taxation and subsidisation on either side. Evidently, even small degrees of subsidisation have a very strong effect on the performance multiplier (more pronounced than the same rate of positive taxation!). This makes subsidisation of qubit expansion highly tempting.

\begin{figure*}[htpb]
\includegraphics[width=0.47\textwidth]{tax_exp}
\includegraphics[width=0.47\textwidth]{tax_subsidy}
\caption{(top) Relationship between the tax performance multiplier, (positive) tax rate, and network size, assuming an exponential computational scaling function, in the regime of positive taxation, \mbox{$\gamma_T>1$}. (bottom) For \mbox{$N_\mathrm{tax}=10$}, a zoom into the region around neutral taxation, where \mbox{$\gamma_T\approx 1$}, showing slight degrees of both taxation (\mbox{$\gamma_T>1$}) and subsidisation (\mbox{$\gamma_T<1$}). Neutral taxation, \mbox{$\gamma_T=1$}, is shown in orange.}\label{fig:tax_exp}\index{Tea party}\index{Don't tread on me}
\end{figure*}

@@

%
% Properties & policy implications of a qubit marketplace
%

\section{Properties \& policy implications of a qubit marketplace}

@@

\subsection{Elasticity of the qubit market \& its policy implications}

@@

The supply side of the equation is also going to be initially highly inelastic. However, as time progresses and technological advancements and enhancements increase the computational power of the quantum internet, the supply of qubits will become increasingly responsive to price fluctuations. However, the extent to how elastic the supply becomes over time is also going to be affected by potential for excess capacity given the exponential trajectory of the manufacture of qubits as new and improved quantum technologies emerge.

@@

The graph indicates a downward sloping demand line, indicating that the lower the price, the higher the demand. The upward sloping supply curve reflects financial incentive, the higher the price, the greater the incentive there is for firms to increase the quantity of qubits available to the market. Correlating this to elasticities, a steeper demand or supply curve indicates a higher degree of inelasticity. As such, in Fig.~\ref{fig:supply_demand}(a)\index{Supply \& demand curve}, the slope of both the demand and supply curves are relatively inelastic (compared to a $45^\circ$ reference line). From this, the imposition of a consumer-based tax can be shown through the vertical shift of the supply curve, with the magnitude of the shift, \mbox{$P_c - P_s$}, indicating the per-qubit value of the tax. Other important observations from the graph are the tax revenue collected (shaded in light teal), the loss of market efficiency through the imposition of a tax (shaded in dark teal), and a relatively small reduction in the quantity of qubits offered on the market from the efficient quantity, $Q_e$, to the quantity with the consumer tax, $Q_t$\index{Taxation}.

\begin{figure*}[htbp]
\includegraphics[width=0.8\textwidth]{supply_demand}
\caption{Hypothetical supply/demand curves, showing the impact of taxation on price and supply, for both inelastic (a) and elastic (b) market dynamics. $Q_e$ and $P_e$ are the efficient market quantity and price of the asset respectively. $P_s$ is the price faced by suppliers, while $P_c$ is the consumer price under taxation. $Q_t$ is quantity in a taxed environment.}\index{Supply \& demand curve}\label{fig:supply_demand}	
\end{figure*}

@@

From a policy implications perspective, this means that governments wanting to cash in on the new technology need to be cautious with the imposition of taxes relative to market maturity. Imposing a significant tax early on may only act as a disincentive to the development of the industry. However, once the market matures further, the imposition of a qubit-tax would make strong economic sense, as there will be minimal loss of market efficiency. Importantly, such a tax on computational power alone could serve to be a relatively stable revenue generation tool for governments.

\section{Game theory of the qubit}\index{Game theory}

\dropcap{T}{he} previous section discussed the implications of the imposition of a tax on the qubit market, assuming it operates in a relatively competitive environment. However, given the massive technological and financial investment made to realise just a single quantum computing system, let alone an entire network, the likely resulting market structure will not be a perfectly competitive one. Rather, just a few significant firms will likely dominate the space, creating a global oligopoly where profit extraction in the face of various taxation frameworks is to be the more likely scenario.

@@

\subsection{The Nash equilibrium \& VNM solution for maximal utility}\index{Nash equilibrium}

@@

	\[\mathrm{Model}\] & \[\mathrm{General form}\] & \[f_\mathrm{sc}(n)=n\] & \[f_\mathrm{sc}(n)=n^p\] & \[f_\mathrm{sc}(n)=e^n\]\\

>>>>

@@

%
% Economic properties of the qubit marketplace
%

\section{Economic properties of the qubit marketplace}

@@

\subsection{Elasticity of the qubit market}

@@

The supply side of the equation is also initially going to be highly inelastic. However, as time progresses and technological advancements and enhancements increase the computational power of the quantum internet, the supply of qubits will become increasingly responsive to price fluctuations \comment{Why?}. However, the extent to how elastic the supply becomes over time is also going to be affected by potential for excess capacity given the exponential trajectory of the manufacture of qubits as new and improved fabrication technologies emerge.

Any asset, dividend, derivative or other financial instrument will inevitably be subject to taxation. Any form of taxation has multiplier effects as the cost markup is repeatedly handed from one market participant to the next, influencing the chain of supply and demand along the way. However, this multiplier and other economic consequences are highly dependent on the asset undergoing transaction -- the economic implications of personal income tax are quite different to those of capital gains tax!

\subsubsection{Computational perspective}

This demonstrates that the computational power of classical networks is simply inversely proportional to the rate of taxation, i.e a linear tax performance multiplier, as we intuitively expect. And for quadratic scaling functions the dependence is inverse quadratic in the taxation rate. In both cases the multiplier is a constant factor, independent of the network size. However, for exponential scaling functions we observe an exponential dependence on both the rate of taxation and the size of the network, shown in Fig.~\ref{fig:tax_exp}(left). Note that for large networks executing computations with exponential scaling functions, there is enormous sensitivity to variations in tax rates, yielding very high leverage in computational return by tax rates.

However, taxation could also be negative, in the form of subsidisation. In Fig.~\ref{fig:tax_exp}(right) we focus on the region surrounding neutral taxation, showing small degrees of taxation and subsidisation on either side. Evidently, even small degrees of subsidisation have a very strong effect on the performance multiplier (more pronounced than the same rate of positive taxation!). This makes subsidisation of qubit expansion highly tempting.

\begin{figure*}[htpb]
\includegraphics[width=0.47\textwidth]{tax_exp}
\includegraphics[width=0.47\textwidth]{tax_subsidy}
\caption{(left) Relationship between the tax performance multiplier, (positive) tax rate, and network size, assuming an exponential computational scaling function, in the regime of positive taxation, \mbox{$\gamma_T>1$}. (right) For \mbox{$N_\mathrm{tax}=10$}, a zoom into the region around neutral taxation, where \mbox{$\gamma_T\approx 1$}, showing slight degrees of both taxation (\mbox{$\gamma_T>1$}) and subsidisation (\mbox{$\gamma_T<1$}). Neutral taxation, \mbox{$\gamma_T=1$}, is shown in orange.}\label{fig:tax_exp}\index{Tea party}\index{Don't tread on me}
\end{figure*}

\subsubsection{Policy perspective}

@@

\begin{figure*}[htbp]
\includegraphics[width=0.8\textwidth]{supply_demand}
\caption{Hypothetical supply/demand curves, showing the impact of taxation on price and supply, for both inelastic (a) and elastic (b) market dynamics. $Q_e$ and $P_e$ are the efficient market quantity and price of the asset respectively. $P_s$ is the price faced by suppliers, while $P_c$ is the consumer price under taxation. $Q_t$ is the quantity in a taxed environment. The net tax revenue collected is shaded in light teal, and the loss of market efficiency through the imposition of taxation is shaded in dark teal.}\index{Supply \& demand curve}\label{fig:supply_demand}	
\end{figure*}

The graph indicates a downward sloping demand line, indicating that the lower the price, the higher the demand. The upward sloping supply curve reflects financial incentive, the higher the price, the greater the incentive there is for firms to increase the quantity of qubits available to the market. Correlating this to elasticities, a steeper demand or supply curve indicates a higher degree of inelasticity. As such, in Fig.~\ref{fig:supply_demand}(a)\index{Supply \& demand curve}, the slope of both the demand and supply curves are relatively inelastic (compared to a $45^\circ$ reference line). From this, the imposition of a consumer-based tax can be shown through the vertical shift of the supply curve, with the magnitude of the shift, \mbox{$P_c - P_s$}, indicating the per-qubit value of the tax. Other important observations from the graph are the tax revenue\index{Tax revenue} collected (shaded in light teal), the loss of market efficiency\index{Market efficiency} through the imposition of a tax (shaded in dark teal), and a relatively small reduction in the quantity of qubits offered on the market from the efficient quantity, $Q_e$, to the quantity with the consumer tax, $Q_t$\index{Taxation}.

@@

From a policy implications perspective, this means that governments wanting to cash in on the new technology need to be cautious with the imposition of taxes relative to market maturity \comment{What does this mean?}. Imposing a significant tax early on may only act as a disincentive to the development of the industry. However, once the market matures further, the imposition of a qubit tax would make strong economic sense, as there will be minimal loss of market efficiency. Importantly, such a tax on computational power alone could serve to be a relatively stable revenue generation tool for governments.

%
% Game theory of the qubit
%

\subsection{Game theory of the qubit}\index{Game theory}

Previously we discussed the implications of the imposition of taxation on the qubit market, assuming it operates in a relatively competitive environment. However, given the massive technological and financial investment made to realise just a single quantum computing system, let alone an entire network, the likely resulting market structure will not be a perfectly competitive one. Rather, just a few significant firms will likely dominate the space, creating a global oligopoly where profit extraction in the face of various taxation frameworks is to be the more likely scenario.

@@

\subsubsection{The Nash equilibrium \& VNM solution for maximal utility}\index{Nash equilibrium}

@@

	\[\mathrm{Model}\] & \[\mathrm{General\, form}\] & \[f_\mathrm{sc}(n)=n\] & \[f_\mathrm{sc}(n)=n^p\] & \[f_\mathrm{sc}(n)=e^n\]\\
